\section*{Prologue}
\setcounter{page}{1}
\pagenumbering{roman}
\fancyfoot[LE,RO]{\thepage}

\lettrine[lines=2, findent=3pt,nindent=0pt]{T}{his} work is part of the doctoral project on quantum information which I started on the sumer of 2013.
This work collects part of the research I have done on these previous years.
I will try to be clear throughout all the thesis such that make it readable for a wider audience as it is possible.
This way I hope it will be readable by any person with a bachelor in science, particularly in physics or at least with a partial knowledge in quantum mechanics.
With that in mind the first and the second chapters will be used to introduce the reader into the context on which this thesis was written as well as the basic notions of quantum metrology, the enveloping field of the present work.
Even though I write this thesis for a broad audience in mind, a basic notion on quantum physics and statistics is needed to follow it properly as I said before.
For instance, I will assume among other things that the reader knows what probability is and which are its properties, or what a quantum state is and what it represents.
I will give references where to find such complementary material when I think is necessary.

This research I publish in a thesis form is part of the work done within the Research Group in qantum information in which Prof.
G\'eza T\'oth is the group leader and principal investigator.
I have to mentions the rest of the members of the group Dr. Philipp Hyllus, Dr. Giuseppe Vitagliano, Dr. I\~nigo Urizar-Lanz, Dr. Zolt\'an Zinbor\'as and Dr. Matthias Kleinmann at the time I was working on the projects of this thesis.
Some of them may still be part of the group and some not.
Apart from the group of G\'eza T\'oth based in Bilbao, Spain, this thesis also collects some work done in collaboration with the Theoretical Quantum Optics, TQO, group lead by Prof. Otfried G\"uhne at the University of Siegen, Germany, and the group of Prof. Carsten Klempt at the Leibniz University in Hannover, based also in Germany.
The last one is an experimental group specialized on the creation of exotic quantum states with very many particles with a variety of applications in quantum technology.

First, we investigate the metrological usefulness of a family of states known as the unpolarized Dicke states, which have boosted the sensitivity of magnetometry when lots of particles are used in the sense that quantum enhancements play a very important role to achieve such a precision.
Second, we investigate possible lower bounds on the quantum Fisher information, a quantity that characterizes the usefulness of a state for quantum metrology, using the theory of Legendre transforms such that we obtain thight lower bounds based on few measurements of the initial quantum state that will be used for metrology.
And last but not least, we investigate the gradient magnetometry, i.e., we develop a theory to study the capablilities of some states to sense the change in space of the magnetic field and we apply that theory to some known states.

Before the thesis work the reader can find the present prologue, the list of publications, the table of contents, and a list of abbreviations, figures and tables.
Then, the thesis starts.
On the first pages one can find a brief dedicatory and acknowledgments followed by the chapters.
The content of the chapters is organized as follows.
First, I start with an introduction to describe the current situation of quantum information especially quantum metrology and I write about the basics of quantum metrology and how it emerges from statics and quantum mechanics.
Second, I present the reader our works in characterizing the family of states known as the unpolarized Dicke states, in optimizing the lower bound for the quantum Fisher information when some expectation values of the states are known and our work in gradient quantum metrology.

\begin{flushright}
  Iagoba Apellaniz

  Bilbao, \today
\end{flushright}
