\lettrine[lines=2, findent=3pt,nindent=0pt]{M}{etrology}, as the science of measuring, has played an essential role for the development of the technology as we know it today.
It studies several aspects of the estimation process, such as which strategy to follow in order to improve the precision of an estimation.
One of the most important figure of merit in this context is the achievable precision for a given system, independently of the strategy.
We will show how to characterize it in the subsequents sections.
And we will show as well different strategies to achieve the desired results.
The metrology science also covers from the design aspects of a precise measuring device, until the most basic concepts of nature which lead in ultimate instance to the better understanding of the whole process.

In this sense, with the discovery of the Quantum Physics and the development of Quantum Mechanics, new doors for advances in metrology were open on the earlies decades of the 19th century.
Later on, the Quantum Theory lead to the so-called field of Quantum Information which merges the notions of the theory of information and computer science, among others subfields, with the quantum mechanics.
The role of the so-named entanglement, an exclusive feature of Quantum Mechanics, is essential in this context.
Its complete understanding has integrated efforts of many researches world wide.
Said this, the entanglement also is in the center of theoretical concepts included in Quantum Metrology.

On the other hand and with the aim of interpreting raw data, there are the statistics, without which many descriptions of the actual and past physical findings would lack of the rigorous interpretation needed for the complexity of data samples.



\subsection{Background on statistics and theory of estimation}
The main mathematical tools used on metrology belong to statistics with an emphasis on the estimation theory. The statistics makes the raw data of some subject under study comprehensible. It can be a set of different heights of a basketball team, or the age of graduated students, or a set of rapidly measured pressures of the air in the front part of a plane in order to estimate the velocity of the plane. It can be anything. The aim of this thesis is not to cover in all detail the subject of statistics, but to give the reader enough knowledge to understand the basis and properly follow this thesis.

\subsection{Quantum Mechanics}
The ubiquitous probabilistic nature of quantum mechanics is reflected on each corner of the field.
This \emph{ambiguity} of a system been quantum is exploited by many recent technologies.

The state

product states

Entanglement

Evolution

Unitary evolution

Markov

Limblad

Measurements

\subsection{Quantum Metrology}

Histograms of quantum states

Merging the probabilistic features of quantum mechanics with the estimation theory is not tibial.

The figure of merit for this purpose is the so-called Quantum Fisher Information.
